Nitric-oxide-feedback to ciliary photoreceptor cells orchestrates UV avoidance in zooplankton

### 2022-05-18 text/Manuscript.Rmd
Figure update

@@

@@

@@

Including Figures

You can add your figures into the rendered document (to define the path, go up one dir from /text and go into /figures):

![Figure 1. Legend goes here](../figures/Figure1.png){width="80%"}

>>>>

![Figure 1. Legend goes here](../figures/Figure1.png){width="100%"}

@@

![Figure 2. Legend goes here](../figures/Figure2.png){width="100%"}

@@

![Figure 3. Legend goes here](../figures/Figure3.png){width="100%"}

@@
